An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2017-03-26 uai2017/paper.tex
update paper

Figure~\ref{fig:gauss_mix_2} shows that {\sc MHminibatch} dominates in terms of
speed and efficiency. The histograms of the (final) minibatch sizes used each
iteration show that our method consumes significantly less data; the
distribution is short-tailed and the mean is 172, more than an order of
magnitude better compared to the other two methods (averages are 12562 and
675008). \textbf{Daniel: Xinlei, these numbers don't match
Figure~\ref{fig:gauss_mix_2} and the figures need to be updated so the scatter
plot has the correct method names and the scaling key, while the histograms have
the correct names and the seaborn background.} We
further ran 10 runs of mixture of Gaussians experiments, and the average and
standard deviation values of the mean minibatch size for {\sc MHminibatch}, {\sc
AustereMH(c)}, {\sc MHSubLhd} are listed in table ~\ref{tab:gaussianres}. Sizes
correspond to the running times of the methods, excluding the likelihood
computation of all data points for {\sc MHSubLhd}, which would drastically
increase running time.

>>>>

Figure~\ref{fig:gauss_mix_2} shows that {\sc MHminibatch} dominates in terms of
speed and efficiency. The histograms of the (final) minibatch sizes used each
iteration show that our method consumes significantly less data; the
distribution is short-tailed and the mean is 172, more than an order of
magnitude better compared to the other two methods (averages are 12562 and
67508). \textbf{Daniel: Xinlei, these numbers don't match
Figure~\ref{fig:gauss_mix_2} and the figures need to be updated so the scatter
plot has the correct method names and the scaling key, while the histograms have
the correct names and the seaborn background.} We
further ran 10 runs of mixture of Gaussians experiments, and the average and
standard deviation values of the mean minibatch size for {\sc MHminibatch}, {\sc
AustereMH(c)}, {\sc MHSubLhd} are listed in table ~\ref{tab:gaussianres}. Sizes
correspond to the running times of the methods, excluding the likelihood
computation of all data points for {\sc MHSubLhd}, which would drastically
increase running time.
